Temporality is Important for Networks of Hospital Patient Transfers

### 2025-04-09 reports/report.qmd
proto exp setup

>>>>

We initialise the state of a simulation by seeding 30 individuals in a single facility.
We then simulate the system forwards in time until a fixed end time.

Each starting facility is looped over to be the starting facility, and realisations are acquired 20 times for each starting facility.
This gives pairs of hitting times between the (known) starting facility and target facility (which we get for all non-starting facilities by the end of the simulation realisation)
